---
title: "Lab 00 - Hello IDS!"
author: "Connor A. Finlay"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Cameron", "Matt", "Ade", 
           "Murray"),
  github_username = c("ca3eron", "s2487351", "ade8724", 
                      "MurrayBone"), 
  colour = c("Blue", "Blue", "Orange", 
             "Light Blue"),
  hobby = c("Photography", "Chess", "Basketball", 
            "Rowing"),
  favourite_number = c(4, 7, 5, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

Blue and its variants seem to be the most popular colours amongst my team, but no obvious correlation between favourite colour and number. 

 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number",
          title = "My team's favourite numbers, ordered by Github username")
```

Still, blue and similar tones dominate my team's preferences, but their favourite colours fail to predicate their favorite numbers. 
### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Because hobbies can be very diverse, there tend to be a wide variety of hobbies within any group of people and, as such, a bar chart will largrly depict several bars of rougly equal height and thus fails to convey meaningful information. The best way to convey this data might just be to list all the responses from the set. 
